Non-kissing and non-crossing complexes \\ for locally gentle algebras

### 2019-06-17 secondPaper/draft/accordionComplexSurfaces.tex
PPP2: comment (iv) of referee.

\begin{definition}
Consider a marked surface~$\bar\surface = (\surface, V \sqcup V\dual)$, where~$V$ and~$V\dual$ are two disjoint sets of marked points so that the points of~$V$ and~$V\dual$ that are on the boundary of~$\surface$ alternate.
A cellular $V$-dissection~$\dissection$ of~$\bar\surface$ and a cellular $V\dual$-dissection~$\dissection\dual$ of~$\bar\surface$ are \defn{dual cellular dissections} if there are pairs of mutually inverse bijections~$V\dual \leftrightarrow \faces(\dissection)$ and~$V \leftrightarrow \faces(\dissection\dual)$, both denoted~$\dual$ in both directions, such that~$\dissection$ has an edge joining its vertices~$u,v \in V$ and separating its faces~$f,g \in  \faces(\dissection)$ if and only if~$\dissection\dual$ has an edge joining its vertices~$f\dual, g\dual \in V\dual$ and separating its faces~$u\dual, v\dual \in \faces(\dissection\dual)$.
\end{definition}

>>>>

\begin{definition}
Consider a marked surface~$\bar\surface = (\surface, V \sqcup V\dual)$, where~$V$ and~$V\dual$ are two disjoint sets of marked points so that the points of~$V$ and~$V\dual$ that are on the boundary of~$\surface$ alternate.
A cellular $V$-dissection~$\dissection$ of~$\bar\surface$ and a cellular $V\dual$-dissection~$\dissection\dual$ of~$\bar\surface$ are \defn{dual cellular dissections} if there are mutually inverse bijections~$V\dual \leftrightarrow \faces(\dissection)$,~$V \leftrightarrow \faces(\dissection\dual)$, and~$\edges(\dissection) \leftrightarrow \edges(\dissection\dual)$,  all denoted by~$\dual$ in both directions, such that
\begin{enumerate}
 \item for each vertex~$v\in V$, the closure of the face~$v\dual$ of~$\dissection\dual$ contains~$v$;
 \item for each vertex~$w\in V\dual$, the closure of the face~$w\dual$ of~$\dissection$ contains~$w$;
 \item for each edge~$e\in \edges(\dissection)$, the edges~$e$ and~$e\dual$ intersect exactly once in their interior; moreover,~$e$ intersects (in their interior) no other edge of~$\dissection\dual$, and~$e\dual$ intersects (in their interior) no other edge of~$\dissection$.
\end{enumerate}

% ~$\dissection$ has an edge joining its vertices~$u,v \in V$ and separating its faces~$f,g \in  \faces(\dissection)$ if and only if~$\dissection\dual$ has an edge joining its vertices~$f\dual, g\dual \in V\dual$ and separating its faces~$u\dual, v\dual \in \faces(\dissection\dual)$.
\end{definition}
